Bootstrapping Multi-atlas Hippocampal Segmentation with \mb

### 2013-05-01 paper.Rnw
ADNI1 boxplot now has nicer labels; correct subfield labels; and a table of method/volume correlations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                             
% ADNI1 Complete 1Yr Dataset Demographics Table 
%                                                                             
<<ADNI1-scr-demographics, echo=F, results="asis",cache=FALSE>>=
# RID < 2000 ensures only ADNI1 patients
yr1 = read.csv("data/ADNI_baseline_volumes/ADNI1_Complete_1Yr_1.5T_11_15_2012.csv")
yr1$VISCODE <- factor(yr1$Visit, levels = c(1,2,3,4), labels=c("bl","m03","m06","m12"))
yr1 = subset(yr1, !grepl("Scaled_2", Description))
yr1 = yr1[,c("RID","VISCODE")]

adnimerge.yr1 = merge(adnimerge, yr1) 
tab <- summary(DX.bl ~ AGE + PTGENDER + PTEDUCAT + PTETHCAT + CDRSB + ADAS13 +
               MMSE, data = adnimerge.yr1, 
               #subset = RID %in% yr1$RID & VISCODE %in% c('bl','m06','m12'),   
               method = "reverse", test=FALSE, overall=TRUE)

@@

levels(error$region) <-list("CA1"="X1", "CA1"="X101", 
                            "Subiculum"="X2","Subiculum"="X102", 
                            "CA4"="X4","CA4"="X104", 
                            "CA2/CA3"="X5","CA2/CA3"="X105", 
                            "Dentate"="X6","Dentate"="X106")
melted = melt(error,id.vars=c("file", "region"))
melted = rename(melted, c("variable"="measure", "value"="percenterr"))
levels(melted$measure) <- list("WA Resampled"="resampled",
                               "MAGeT + WA Resampled" = "mb_0.9mm",
                               "MAGeT + WA BRAVO"="mb_bravo")

@@

\begin{figure}[h]
<<ADNI-scr-volumes-boxplot,dependson='ADNI-baseline-volumes-prep',cache=T,fig.width=6,fig.height=4>>=
snt.tests <- ddply(totals.complete, c("DX"), function(df) {
  data.frame( corr = cor(df$SNT, df$MAGeT),
              value = -Inf) 
})

qplot(DX,value,data=melt(totals.complete,measure.vars=c("FS", "FSL", "MAPER","MAGeT","SNT")),
      colour=variable,geom="boxplot") + 
      geom_text(aes(y=value,x=DX, vjust=-1.4, size=1,
                    label=paste("r==", signif(corr, digits=3))), 
            colour='black',parse=TRUE, data=snt.tests) +
      xlab("Diagnosis") + ylab("Total Hippocampal Volume (mm3)")
@
  \caption{Comparison of hippocampus volumes obtained by FreeSurfer (FS), FSL, 
  MAPER, \mb (MAGeT) and manual (SNT).}
  \label{fig:ADNI-scr-volumes-boxplot}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                             
% ADNI1 Complete 1Yr Dataset Demographics Table 
%                                                                             
<<ADNI1-scr-demographics, echo=F, results="asis",cache=FALSE>>=
# RID < 2000 ensures only ADNI1 patients
yr1 = read.csv("data/ADNI_baseline_volumes/ADNI1_Complete_1Yr_1.5T_11_15_2012.csv")
yr1$VISCODE <- factor(yr1$Visit, levels = c(1,2,3,4), labels=c("bl","m03","m06","m12"))
yr1 = subset(yr1, !grepl("Scaled_2", Description))
yr1 = yr1[,c("RID","VISCODE")]
yr1 = 
adnimerge.yr1 = merge(adnimerge, yr1) 
tab <- summary(DX.bl ~ AGE + PTGENDER + PTEDUCAT + PTETHCAT + CDRSB + ADAS13 +
               MMSE, data = adnimerge.yr1, 
               #subset = RID %in% yr1$RID & VISCODE %in% c('bl','m06','m12'),   
               method = "reverse", test=FALSE, overall=TRUE)

@@

levels(error$region) <-list("CA1"="X1", "CA1"="X101", 
                            "Subiculum"="X2","Subiculum"="X102", 
                            "CA4/DG"="X4","CA4/DG"="X104", 
                            "CA2/CA3"="X5","CA2/CA3"="X105", 
                            "SR/SL/SM"="X6","SR/SL/SM"="X106")
melted = melt(error,id.vars=c("file", "region"))
melted = rename(melted, c("variable"="measure", "value"="percenterr"))
levels(melted$measure) <- list("Subsampled"="resampled",
                               "MAGeT + Subsampled" = "mb_0.9mm",
                               "MAGeT + BRAVO"="mb_bravo")

@@

\begin{figure}[h]
<<ADNI-scr-volumes-boxplot,dependson='ADNI-baseline-volumes-prep',cache=T,fig.width=6,fig.height=4>>=
qplot(DX,value,data=melt(totals.complete,measure.vars=c("FS", "FSL", "MAPER","MAGeT","SNT")),
      colour=variable,geom="boxplot") + 
      #geom_text(aes(y=value,x=DX, vjust=-1.4, size=1,
      #              label=paste("r==", signif(corr, digits=3))), 
      #      colour='black',parse=TRUE, data=snt.tests) +
      xlab("Diagnosis") + 
      ylab(expression(paste("Total hippocampal volume (", mm^3, ")")))
@
  \caption{Comparison of hippocampus volumes obtained by FreeSurfer (FS), FSL, 
  MAPER, \mb (MAGeT) and manual (SNT).}
  \label{fig:ADNI-scr-volumes-boxplot}
\end{figure}

\begin{figure}[h]
<<ADNI-scr-volumes-plot,dependson='ADNI-baseline-volumes-prep',cache=T,fig.width=6,fig.height=4>>=
melted=melt(totals.complete, measure.vars=c("FS", "FSL", "MAPER","MAGeT"), 
            variable.name = "method", value.name = "volume")

snt.tests <- ddply(totals.complete, c("DX"), function(df) {
  data.frame( corr = cor(df$SNT, df$MAGeT),
              value = -Inf) 
})

ggplot(data=melted, aes(x=SNT, y=volume, colour=method)) + 
      geom_point() + 
      geom_smooth(method="lm") + 
      #geom_text(aes(y=value,x=DX, vjust=-1.4, size=1,
      #              label=paste("r==", signif(corr, digits=3))), 
      #      colour='black',parse=TRUE, data=snt.tests) +
      xlab(expression(paste("Manual total hippocampal volume (", mm^3, ")"))) + 
      ylab(expression(paste("Total hippocampal volume (", mm^3, ")")))
@
  \caption{Comparison of hippocampus volumes obtained by FreeSurfer (FS), FSL, 
  MAPER, \mb (MAGeT) and manual (SNT).}
  \label{fig:ADNI-scr-volumes-plot}
\end{figure}

<<ADNI-scr-volumes-table,dependson='ADNI-baseline-volumes-prep',cache=T,results='asis'>>=
melted=melt(totals.complete, measure.vars=c("FS", "FSL", "MAPER","MAGeT"), 
            variable.name = "method", value.name = "volume")

snt.tests <- ddply(totals.complete, c("DX"), function(df) {
  round(data.frame( MAGeT = cor(df$SNT, df$MAGeT),
              MAPER = cor(df$SNT, df$MAGeT),
              FS    = cor(df$SNT, df$FS),
              FSL   = cor(df$SNT, df$FSL)
              ), 2)
})

latex(snt.tests, #file="", 
      size="scriptsize",
      caption="", row.names="",
      title="")
@
